surface-insitu

### 2025-03-12 README.Rmd
readme
new logo! TORF!
fix #18 #16 #12, rename torf,

---
title: "R Tools for Obspack, Receptors and Footprints (rtorf)"
output: github_document
---

@@

@@

[NOAA Obspack](https://gml.noaa.gov/ccgg/obspack/) is a collection of green house gases observations

@@

obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, categories = cate)

@@

```{r, include=F}
data.frame(
  stringsAsFactors = FALSE,
  R = c("fex","invfile",
        "obs_addltime","obs_addstime","obs_addtime","obs_agg",
        "obs_find_receptors","obs_footname","obs_format","obs_freq",
        "obs_index","obs_invfiles","obs_list.dt","obs_meta",
        "obs_out","obs_plot","obs_rbind","obs_read","obs_read_csvy",
        "obs_read_nc","obs_roundtime","obs_summary",
        "obs_table","obs_trunc","obs_write_csvy","plot.invfile",
        "print.invfile","sr","summary.invfile"),
  description = c("File extension",
                  "Methods for objects with class 'invfile'",
                  "local hour (bsed on longitude and time)","Add solar time into obspack",
                  "Add times into obspack","Aggregates ObsPack by time",
                  "Compares expected receptors","Expected footprint name",
                  "Formatting data","return numeric vector in intervals",
                  "Summary of the ObsPack files (.txt)",
                  "Generate files to perform inverse modeling","list.dt","Read obspack metadata",
                  "outersect","Read obspack metadata","rbind obspack",
                  "Read obspack (.txt)","reads CSVY","Read obspack (.nc)",
                  "round seconds from \"POSIXct\" \"POSIXt\" classes",
                  "Summary of the ObsPack files (.txt)","Obspack Table",
                  "Trunc numbers with a desired number of decimals",
                  "Generates YAML and write data.frame",
                  "Methods for objects with class 'invfile'","Methods for objects with class 'invfile'",
                  "Extacts n last characters",
                  "Methods for objects with class 'invfile"),
  Python = c("","","","","","","","",
             "","","OK","","","","","","","","","OK","",
             "","","","","","","","")
) -> df

```{r, eval=TRUE, echo=FALSE}
knitr::kable(df)

```
## Special thanks to all the contributors

>>>>

---
title: "R Tools for Observations, Receptors and Footprints (rtorf)"
output: github_document
---

@@

<img src="man/figures/logo.png" align="right" alt="" width="220" />

@@

[NOAA Obspack](https://gml.noaa.gov/ccgg/obspack/) is a collection of greenhouse gases observations

@@

obs <- "Z:/obspack/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, categories = cate)

@@

## Special thanks to all the contributors

### 2025-03-12 examples/aircraft-pfp.Rmd
fix #18 #16 #12, rename torf,

obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

@@

```{r readnc, eval = T}
datasetid <- "aircraft-pfp"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

>>>>

obs <- "Z:/obspack/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

@@

```{r readnc, eval = T}
datasetid <- "aircraft-pfp"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  verbose = T)

### 2025-03-12 examples/shipboard-flask.Rmd
check articles
fix #18 #16 #12, rename torf,

obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

Now we read the surface-flask using the function `obs_read_nc`. 
`solar_time` is  included for surface, so we `TRUE` that argument.

>>>>

obs <- "Z:/obspack/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

Now we read the `shipboard-flask` using the function `obs_read_nc`. 
`solar_time` is  included for surface, so we `TRUE` that argument.

### 2025-03-12 examples/surface-insitu.Rmd
check articles
fix #18 #16 #12, rename torf,

obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

Now we read the surface-insitu using the function `obs_read_nc`. 
`solar_time` is  included for surface, so we `TRUE` that argument.

>>>>

obs <- "Z:/obspack/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

Now we read the `surface-insitu` using the function `obs_read_nc`. 
`solar_time` is  included for surface, so we `TRUE` that argument.
